Reconstructing Propositional Proofs in Type Theory

### 2017-10-24 paper/sections/proof-reconstruction.tex
[ paper ] fixing last suggestions.
[ paper ] fixing refs.

In this section, we reconstruct each \Metis inference rule with a
function and its respective theorem. We present a pattern of the
formal description for these rules.

@@

\begin{myexample}
\Metis has a inference rule named conjunct.
Since that rule appears in \TSTP derivations like in the following excerpt.
We refer to this rule writing \conjunct.

@@

\subfile{sections/proof-reconstruction/strip.tex}
\subfile{sections/proof-reconstruction/negate.tex}
\subfile{sections/proof-reconstruction/conjunct.tex}
\subfile{sections/proof-reconstruction/resolve.tex}
\subfile{sections/proof-reconstruction/canonicalize.tex}
\subfile{sections/proof-reconstruction/clausify.tex}
\subfile{sections/proof-reconstruction/simplify.tex}

>>>>

In this section, we reconstruct each \Metis inference rule
in Table~\ref{tab:agda-metis-table} with a
function and its respective theorem. We present a pattern of the
formal description for these rules.

@@

\begin{myexample}
\Metis has a inference rule named conjunct.
We refer to this rule writing \conjunct.

@@

\subfile{sections/proof-reconstruction/strip.tex}
\subfile{sections/proof-reconstruction/conjunct.tex}
\subfile{sections/proof-reconstruction/resolve.tex}
\subfile{sections/proof-reconstruction/canonicalize.tex}
\subfile{sections/proof-reconstruction/clausify.tex}
\subfile{sections/proof-reconstruction/simplify.tex}
